Notes on Twisted SYM

### 2019-01-09 10-9-8d_twists_1_19.tex
some more 8d edits

\begin{example}[9d $\mc N=1$ Super Yang-Mills]
Let's decompose our fields further into irreducible summands with respect to the action of $\SU(4)$.  We also restrict to 10d fields which are constant in the $x^{10}$-direction.  The only fields we'll consider are those which survived the 10d holomorphic twist.  These fields are
\begin{align*}
B^{10} &= B + A \wedge \d x^9 \in (\Omega^{0,2}(\CC^4; \gg) \oplus \Omega^{0,1}(\CC^4; \gg)) \otimes \Omega^0(\RR_9) \\
A^{10}_{0,1} &= A' + \phi \d x^9 \in (\Omega^{0,1}(\CC^4; \gg) \oplus \Omega^0(\CC^4; \gg)) \otimes \Omega^0(\RR_9)
\end{align*}
along with the ghost $c$.

@@

\begin{enumerate}
\item The latter -- the partially topological twist -- is acted upon by $\SU(3)$.  Again, let's decompose our twisted component fields with respect to the action of $\SU(3)$, and restrict to fields which are constant in the $x^{10}$ and $x^9$ directions.  The result is
\begin{align*}
B^{10} &= B + A_2 + A_3 + \phi_1 \in (\Omega^{0,2}(\CC^3; \gg) \oplus \Omega^{0,1}(\CC^3; \gg)^2\oplus \Omega^0(\CC^3; \gg)) \otimes \Omega^0(\RR_7 \times \RR_8)\\
A^{10}_{0,1} &= A_1 + \phi_2 + \phi_3 \in (\Omega^{0,1}(\CC^3; \gg) \oplus \Omega^0(\CC^3; \gg)^2) \otimes \Omega^0(\RR_7 \times \RR_8)
\end{align*}
again, along with the ghost $c$ (I've skipped writing the $\d x^7$ and $\d x^8$ factors in here).

@@

\item The former -- the holomorphic twist -- is essentially equivalent to the theory discussed in dimension 9, but without the $\Omega^0(\RR_9)$ factor.  It is still acted upon by $\SU(4)$.  This theory should be a cotangent theory where the base -- in terms of BV fields -- is spanned by $c, A, \st B, \st A', \st \phi$, and the fiber is spanned by $\phi, A', B, \st A, \st c$.  We can see this by thinking about which fields are bosonic and which are fermionic.  This example should, for the first time, be promotable into a $\ZZ$-graded theory.  For this to produce the correct degrees, we need $A'$ to have R-symmetry weight $-1$ and $\phi$ to have R-symmetry weight $-2$.  I don't see right now where this is supposed to come from.
\end{enumerate}

>>>>

\begin{example}[9d $\mc N=1$ Super Yang-Mills]
Let's decompose our fields further into irreducible summands with respect to the action of $\SU(4)$.  We also restrict to 10d fields which are constant in the $x^{10}$-direction.  The only fields we'll consider are those which survived the 10d holomorphic twist.  These fields are
\begin{align*}
B^{10} &= B + A \wedge \d \ol z^5 \in (\Omega^{0,2}(\CC^4; \gg) \oplus \Omega^{0,1}(\CC^4; \gg)) \otimes \Omega^0(\RR_9) \\
A^{10}_{0,1} &= A' + \phi \d \ol z^5 \in (\Omega^{0,1}(\CC^4; \gg) \oplus \Omega^0(\CC^4; \gg)) \otimes \Omega^0(\RR_9)
\end{align*}
along with the ghost $c$.

@@

\begin{enumerate}
\item The latter -- the partially topological twist -- is acted upon by $\SU(3)$.  Again, let's decompose our twisted component fields with respect to the action of $\SU(3)$, and restrict to fields which are constant in the $x^{10}$ and $x^9$ directions.  The result is
\begin{align*}
B^{10} &= B + A_2 + A_3 + \phi_1 \in (\Omega^{0,2}(\CC^3; \gg) \oplus \Omega^{0,1}(\CC^3; \gg)^2\oplus \Omega^0(\CC^3; \gg)) \otimes \Omega^0(\RR_7 \times \RR_8)\\
A^{10}_{0,1} &= A_1 + \phi_2 + \phi_3 \in (\Omega^{0,1}(\CC^3; \gg) \oplus \Omega^0(\CC^3; \gg)^2) \otimes \Omega^0(\RR_7 \times \RR_8)
\end{align*}
again, along with the ghost $c$ (I've skipped writing the $\d \ol z^4$ and $\d \ol z^5$ factors in here).

@@

\item The former -- the holomorphic twist -- is essentially equivalent to the theory discussed in dimension 9, but without the $\Omega^0(\RR_9)$ factor.  It is still acted upon by $\SU(4)$.  This theory should be a cotangent theory where the base -- in terms of BV fields -- is spanned by $c, A', B, \st A, \st \phi$, and the fiber is spanned by $\phi, A, \st B, \st A', \st c$.  We can see this by thinking about which fields are bosonic and which are fermionic.  This example should, for the first time, be promotable into a $\ZZ$-graded theory.  For this to produce the correct degrees, we need the following R-charges under the 8d $\CC^\times$ R-symmetry group:
\begin{align*}
B &\text{: charge } +1 \\
A &\text{: charge } -1 \\
A' &\text{: charge } 0 \\
\phi &\text{: charge } -2. \\
\end{align*}
In 10-dimensions, $A^{10}$, and hence $A_{0,1}^{10}$, has R-charge 0, and $\lambda$, and hence $B^{10}$, has R-charge $+1$.  So writing $A_{0,1}^{10} = A' + \phi \d \ol z^5$ and $B^{10} = B + A \wedge \d \ol z^5$ we get the correct R-charges if $\d \ol z^5$ has R-charge 2.

\end{enumerate}
